Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-26 paper/galsize_paper.tex
Minor edits to section 6

To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples. In the left panels of Figure \ref{fig:lensingprediction}, we show predictions of the $\rvir-$based model for future measurements of $\Delta\Sigma.$ The halo model principles underlying the lensing trends are the same as for $\wproj.$ For $\mstar\lesssim10^{11}\msun,$ the difference in $F_{\rm sat}$ between small and large samples is the dominant factor; satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples. At sufficiently large stellar mass $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10-15\%,$ the role of centrals becomes dominant; the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals, which is reflected in the reversal of the small-scale signal in the bottom left panel.

The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass, $\mhost,$ for small and large samples;\footnote{We calculated the PDFs shown in Figure \ref{fig:lensingprediction} using the Scipy implementation of Gaussian kernel density estimation \citep{scipy}.} for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo. The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites. At all stellar masses, the blue histograms peak at slightly larger $\mhost$ relative to the red; this is because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals. For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values. Qualitatively, these features are completely generic predictions of the $\rvir-$based model; quantitatively, the precise value of $\mstar$ where the effect of centrals begins to dominate $\Delta\Sigma$ depends sensitively on $F_{\rm sat}(\mstar),$ which we have only roughly calibrated in the present work.

>>>>

To date, the $\rhalf-$dependence of $\Delta\Sigma$ has not yet been measured for $\mstar-$complete samples. In the left panels of Figure \ref{fig:lensingprediction}, we show predictions of the $\rvir-$based model for future measurements of $\Delta\Sigma.$ The halo model principles underlying the lensing trends are the same as for $\wproj.$ For $\mstar\lesssim10^{11}\msun,$ the difference in $F_{\rm sat}$ between small and large samples is the dominant factor; satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples. At sufficiently large stellar mass $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10-15\%,$ the role of centrals becomes dominant; the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals, which is reflected in the reversal of the small-scale signal in the bottom left panel.

The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass, $\mhost,$ for small and large samples; for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo. The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites. At all stellar masses, the distributions in blue peak at slightly larger $\mhost$ relative to the red; this is because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals. For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values. Qualitatively, these features are completely generic predictions of the $\rvir-$based model; quantitatively, the precise value of $\mstar$ where the effect of centrals begins to dominate $\Delta\Sigma$ depends sensitively on $F_{\rm sat}(\mstar),$ which we have only roughly calibrated in the present work.
